\section{Applications of MS outside nuclear force theory}

Mass spectrometry has a long history and wide adoption out with nuclear physics both in research and commercially.
MS are essential for chemical analysis – often used to determine the isotopes present in a mixture.
In chemical and biomedical research, they are used frequently for structural elucidation where MS can give information about molecular structure. \cite{bhattarai_chapter_2020}

\subsection{Penning traps and neutrino physics}
One exciting area of study where MS are fundamental is neutrino physics.
The neutrino is the most abundant particle with mass - roughly a thousand trillion pass through your body every second. \cite{noauthor_whats_nodate}
Yet the incredibly light particles are elusive and difficult to detect as they only interact with the weak force and gravity so surprisingly little is known about them. \cite{noauthor_what_nodate}
Research in neutrino science could further the understanding of the standard model and they could be important in explaining why there is matter in the universe and not antimatter \cite{gibney_morphing_2015} – it is thought that neutrinos could be their own antimatter, unlike any other fermion in the standard model \cite{blaum_precision_2012}. 
Penning traps are especially suited to this study due to their high (precison/resolving power).
Since neutrinos are chargeless themselves, an upper limit to their rest mass can be measured by the mass difference between mother and daughter nucleotides from a nuclear decay. \cite{eliseev_penning-trap_2013}
For example the $\beta$ -decay: $^{187}Re \longrightarrow ^{187}Os + e^- + \bar{\nu _e}$ with Rhenium as the mother nucleotide and Osmium the daughter. \cite{repp_pentatrap_2012}
The current upper limit of this mass is 1.
1eV measured at the Karlsruhe Tritium Neutrino (KATRIN) spectrometer. \cite{castelvecchi_physicists_2019}
Although KATRIN is an electron spectrometer and not a MS, PENTATRAP is a new five Penning trap facility being built in Heidelberg, Germany and is expected to reduce this upper mass limit even further \cite{repp_pentatrap_2012}.

\subsection{MR-TOF's applications outside physics}
MR-TOF MS also have many applications outside nuclear physics.
Due to their compact size and relative affordability compared to Penning traps, MR-TOF's are suited to \emph{in situ} applications \cite{dickel_multiple-reflection_2013}.
One potential application is waste water management where the MS could identify pollutants \cite{dickel_multiple-reflection_2013} – during COVID-19 pandemic waste water analysis was used to model the spread of the disease \cite{noauthor_wastewater_nodate}.
One current application of the technology is in biomedical analysis where a variation of the device (MALDI-TOF MS) is used routinely as an accurate and fast method to identify of microorganisms which reduces costs as it requires minimum consumables. \cite{noauthor_uk_2019}